---
title: "Beers and Breweries Analysis"
author:
- Luke Pierce <lepierce@smu.edu>
- Lokesh Maganti <lmaganti@smu.edu>
- Andrew Walch <awalch@smu.edu>
- MJKelleher <mikek@smu.edu>
date: "February 14, 2018"
output:
  html_document:
    toc: yes
    toc_depth: 2
  word_document:
    toc: yes
    toc_depth: '2'
  pdf_document:
    toc: yes
    toc_depth: '2'
subtitle: Case Study 01 - MSDS 6306 Section 402
---

```{r setup, include=FALSE, echo=TRUE}
# Clean the workspace, remove all existing Objects
rm(list=ls())
```

```{r, results='hide', message=FALSE, warning=FALSE, echo=FALSE}
library(knitr)
# Set RMarkdown plots to a default 12 by 8 inches
knitr::opts_chunk$set(fig.width=12, fig.height=8)
```

<!-- Include the Introduction Rmd file -->
```{r child = 'rmd/Introduction.rmd'}
```

<!-- Include the Answers Rmd file -->
```{r child = 'rmd/Answers.rmd'}
```

<!-- Include the Conclusion Rmd file -->
```{r child = 'rmd/Conclusion.rmd'}
```

<!-- Include the Codebook Rmd file -->
```{r child = 'rmd/Codebook.rmd'}
```

## Appendix
### File Definitions
- Project Directories, Documentation, Source Code, Data
    - <Project Root>/
        - MSDS_6306_Sect_402_Case_Study_01.Rmd
            - The main RMarkdown file.  Use this file to knit the report.
        - MSDS_6306_Sect_402_Case_Study_01.html
            - This is the knitted report.
        - README.md
            - The file you are looking at right now.
        - Solution.R
            - This is the same R code to produce the results, minus all of the RMarkdown.
        - Writeup_CaseStudy1_LEP_v1.txt
            - TODO: define what this is
        - Tidy_Recipe.R
            - If you want to just build the tidy dataset, run this file.
        - Case_Study_code_file_v1
            - TODO: define what this is, move it to archive, or delete it.
        - resources.txt
            - TODO: define what this is, move it to archive, or delete it.
        - CaseStudy1.pdf
            - TODO: define what this is, move it to archive, or delete it.
    - archive/
        - Exactly what is says.
    - code/
        - Re-usable chunks of code used in both the main project Rmd file, the Solution.R file and Tidy_Recipe.R.
        - 00_Setup.R
            - This sets the R environment up for the all of the analyses to be run.
        - 00_LoadAndPrepare.R
            - Loads the data, and prepares it for analysis.
        - 01_Question_01.R
            - Performs the operations to answer the first question.
        - 01_Question_01.tidy.R
            - Performs the oprations to create the tidy dataset needed for Question 1, and all other questions.
        - 02_Question_02.R
            - Performs the operations to answer the second question.
        - 02_Question_02.tidy.R
            - Performs the oprations to create the tidy dataset needed for Question 2, and all other questions.
        - 03_Question_03.R
            - Performs the operations to answer the third question.
        - 03_Question_03.tidy.R
            - Performs the oprations to create the tidy dataset needed for Question 3, and all other questions.
        - 04_Question_04.R
            - Performs the operations to answer the fourth question.
        - 05_Question_05.R
            - Performs the operations to answer the fifth question.
        - 06_Question_06.R
            - Performs the operations to answer the sixth question.
        - 07_Question_07.R
            - Performs the operations to answer the seventh question.
    - rmd/
        - Files in this directory are included into the main file when the document is knitted together.  They are here mainly for organizational purposes.
        - Answers.Rmd
            - Human readable, textual answers in prose form.  These are the formal answers the the posed questions.
        - Codebook.Rmd
            - The codebook, defining the uncleaned data, as well as the tidy data.
        - Introduction.Rmd
            - Project introduction.
    - data/
        - Breweries.csv
        - Beers.csv
Directories not managed by Git
- data/tidy/  :  This is where the tidy dataset are stored when they are created by running the Analysis.  This is transient storage.
- tmp/        :  Transient storage for graphics and other intermediary files.

### Source Code
#### Required Libraries
1. deplyr    - To Install: `install.packages("deplyr")`
1. ggplot2   - To Install: `install.packages("ggplot2")`
1. doBy      - To Install: `install.packages("doBy")`
1. stringr   - To Install: `install.packages("stringr")`
1. reshape2  - To Install: `install.packages("reshape2")`
1. gridExtra - To Install: `install.packages("gridExtra")`

#### Case Study Solution

```{r, results='hide', message=FALSE, warning=FALSE}
#
# NOTE:
# If you add any libraries to this file, make sure you add the library to the
# 'ENVIRONMENT' section of the file: code/00_LoadAndPrepare.R
#
library(dplyr)
library(ggplot2)
library(doBy)
library(stringr)
library(reshape2)
library(gridExtra)
```

```{r, results='hide', message=FALSE, warning=FALSE, echo=FALSE}
#
# This imports the R scripts, but does not execute them yet.
# They are executed later in the next code chunk
read_chunk('code/00_LoadAndPrepare.R')
read_chunk('code/01_Question_01.R')
read_chunk('code/02_Question_02.R')
read_chunk('code/03_Question_03.R')
read_chunk('code/04_Question_04.R')
read_chunk('code/05_Question_05.R')
read_chunk('code/06_Question_06.R')
read_chunk('code/07_Question_07.R')

#
# In RStudio the next block of code may look like it has a compile or syntax
#    error in the editor.  However, if you run 'Knit', the document will build
#    without error.  It will give you and error:  "Unexpected token '<'"
#
```


```{r}
<<LoadAndPrepare>>
<<Question_01>>
<<Question_02>>
<<Question_03>>
<<Question_04>>
<<Question_05>>
<<Question_06>>
<<Question_07>>
```
