---
title: "Beers and Breweries Analysis"
subtitle: "Case Study 01 - MSDS 6306 Section 402"
author:
- Luke Pierce <lepierce@smu.edu>
- Lokesh Maganti <lmaganti@smu.edu>
- Andrew Walch <awalch@smu.edu>
- MJKelleher <mikek@smu.edu>
date: "February 14, 2018"
output: 
  html_document:
    toc: true
    toc_depth: 2
  pdf_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE, echo=TRUE}
# Clean the workspace, remove all existing Objects
rm(list=ls())
source('code/00_Setup.R')
```

```{r, results='hide', message=FALSE, warning=FALSE, echo=FALSE}
library(knitr)
# Set RMarkdown plots to a default 12 by 8 inches
knitr::opts_chunk$set(fig.width=12, fig.height=8)
```

<!-- Include the Codebook Rmd file -->
```{r child = 'rmd/Codebook.rmd'}
```

<!-- Include the Introduction Rmd file -->
```{r child = 'rmd/Introduction.rmd'}
```

<!-- Include the Answers Rmd file -->
```{r child = 'rmd/Answers.rmd'}
```

## Conclusion
TODO: Add conclusion here

## Appendix
### Source Code
#### Required Libraries
1. deplyr    - To Install: `install.packages("deplyr")`
1. ggplot2   - To Install: `install.packages("ggplot2")`
1. doBy      - To Install: `install.packages("doBy")`
1. stringr   - To Install: `install.packages("stringr")`
1. reshape2  - To Install: `install.packages("reshape2")`
1. gridExtra - To Install: `install.packages("gridExtra")`

#### Case Study Solution

```{r, results='hide', message=FALSE, warning=FALSE}
#
# NOTE:
# If you add any libraries to this file, make sure you add the library to the
# 'ENVIRONMENT' section of the file: code/00_LoadAndPrepare.R
#
library(dplyr)
library(ggplot2)
library(doBy)
library(stringr)
library(reshape2)
library(gridExtra)
library(gplots)
```

```{r, results='hide', message=FALSE, warning=FALSE, echo=FALSE}
#
# This imports the R scripts, but does not execute them yet.
# They are executed later in the next code chunk
read_chunk('code/00_LoadAndPrepare.R')
read_chunk('code/01_Question_01.R')
read_chunk('code/02_Question_02.R')
read_chunk('code/03_Question_03.R')
read_chunk('code/04_Question_04.R')
read_chunk('code/05_Question_05.R')
read_chunk('code/06_Question_06.R')
read_chunk('code/07_Question_07.R')

#
# In RStudio the next block of code may look like it has a compile or syntax
#    error in the editor.  However, if you run 'Knit', the document will build
#    without error.  It will give you and error:  "Unexpected token '<'"
#
```


```{r}
<<LoadAndPrepare>>
<<Question_01>>
<<Question_02>>
<<Question_03>>
<<Question_04>>
<<Question_05>>
<<Question_06>>
<<Question_07>>
```
